Direct observation of Feshbach enhanced \swave{} scattering of fermions

### 2015-09-02 draft1.tex
Changed abstract after William's comments

\begin{abstract}
We directly measured the \swave{} scattering cross-section of ultracold \K{} atoms across the 20.2 \mT{} Feshbach resonance by colliding pairs of degenerate Fermi gases (DFGs) and imaging the scattered atoms. Owing to DFG's low density, few atoms scattered, even near the resonance. To optimize signal to noise, we developed techniques to interpret absorption images in the regime where recoil induced
detuning corrections are significant. By applying these techniques to our \swave{} scattering data we extracted the resonant magnetic
field value  $B_0 = 20.247(2)$  \mT{} and resonance width $\Delta = 1.0(1)$  \mT{}. These imaging techniques are generally applicable to experiments with light atoms in which maximizing the signal-to-noise ratio on the atom number counting is critical and imaging resolution can be sacrificed.
\end{abstract}

>>>>

\begin{abstract}
We directly measured the \swave{} scattering cross-section of ultracold \K{} atoms across the 20.2 \mT{} Feshbach resonance by colliding pairs of degenerate Fermi gases (DFGs) and imaging the scattered atoms.  We developed techniques to interpret absorption images in the regime where recoil induced detuning corrections are significant, and used those techniques to optimize the signal-to-noise ratio of atom number in scattering images. We extracted the scattered fraction for a range of bias magnetic field settings, and obtained a measurement of the Feshbach resonance's field location and width. These imaging techniques are generally applicable to experiments with lighter alkalis that would benefit from maximizing signal-to-noise ratio on the atom number counting at the expense of spatial imaging resolution.
\end{abstract}
